Manuscript Figures for Genome Biology

### 2018-07-17 manuscript_figures/manuscript_figures.Rmd
Add draft prototype figure of uninformative covariate impact in Yeast and Polyester *within replicate*

>>>>

# Informativeness of covariates in Yeast simulation

As an alternative to the line plot above (Figure S7), we make a heatmap plot that
displays the mean difference within simulation replicate.

```{r}

objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) ]

# regexp to construct master data table separating case study datasets, methods
# and covariates
obj.names <- str_split(resfile, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
filename <- gsub(".rds", "", unlist(lapply(obj.names, function(x) x[4] )))
dataset <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[3]]))
inform <-  ifelse(grepl("uninf", resfile), "uninf", "inf")
type <-  ifelse(grepl("null", resfile), "null", "de")
size <-  ifelse(grepl("10", resfile), "10", "5")

tab <- data.frame()
for (l in seq_along(resfile)){
  x <- readRDS(resfile[l])

  tmp2 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                 fill =  "FDR", annotate = NULL, alpha = 0.10) %>%
    mutate(fdr = nrejects) %>%
    select(method, casestudy, replicate, fdr)
  tmp3 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                  fill =  "TNR", annotate = NULL, alpha = 0.10) %>%
    mutate(tnr = nrejects) %>%
  select(method, casestudy, replicate, tnr)

  if (type[l] != "null"){
    tmp1 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                    fill =  "TPR", annotate = NULL, alpha = 0.10) %>%
      mutate(tpr = mean(nrejects)) %>%
    select(method, casestudy, replicate, tpr)

    tmp <- left_join(tmp1, tmp2, by = c("method", "casestudy", "replicate")) %>%
      left_join(tmp3, by = c("method", "casestudy", "replicate")) %>%
      mutate(inform = inform[l],
             type = type[l],
             size = size[l])
  }else{
    tmp <- left_join(tmp2, tmp3, by = c("method", "casestudy", "replicate")) %>%
      mutate(inform = inform[l],
             type = type[l],
             size = size[l])
  }

  tab <- bind_rows(tab, tmp)
}

# take difference within replicate, then average differences across
# type and size and method

dftab <- tab %>%
  filter(method %in% cov.methods) %>%
  dplyr::mutate(id = paste(type, size, method, replicate, sep = "-"))

uninftab <- dftab %>% 
  filter(inform == "uninf") %>%
  select(id, fdr, tpr, tnr) %>%
  rename(fdr_uninf = fdr,
         tnr_uninf = tnr,
         tpr_uninf = tpr)

dftab <- left_join(inftab, uninftab, by = "id") %>%
  mutate(tpr_diff = tpr-tpr_uninf,
         fdr_diff = fdr-fdr_uninf,
         tnr_diff = tnr-tnr_uninf) %>%
  group_by(type, size, method) %>%
  summarize(tpr_diff = mean(tpr_diff),
            fdr_diff = mean(fdr_diff),
            tnr_diff = mean(tnr_diff)) %>%
  mutate(method = factor(method, levels = rowOrder))

plot_fun <- function(var){

  plot  <- ggplot(dftab %>% filter(!is.na(get(var))), 
                  aes(x = interaction(type, size), 
                                        y = method)) + 
    geom_tile(aes(fill=get(var))) + 
    scale_fill_distiller(paste0("Change\nin ", toupper(var)),
                         palette = "Blues", direction = 1,
                         labels = scales::percent) +
    theme_bw() +
    xlab("Experiment") +
    ylab("Method") +
    facet_grid( ~ type + size, scales = "free", space = "free") +
    ggtitle(paste0("Impact of informative covariate on ", toupper(var))) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
        legend.justification = c(1, 1),
        legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 9),
        legend.margin = margin(6, 10, 6, 10)) +
    geom_text(aes(label = scales::percent(get(var))),
            color = "black", size = 3)

  return(plot)
}

plot_fun("tpr_diff")
plot_fun("fdr_diff")
plot_fun("tnr_diff")
```
